---
title: "Hello R"
author: "Nicholas Solis"
date: "Data 2401"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```
### Exercise 1
the data frame has 1846 rows and 3 columns. The variables included are x and y

### Exercise 2


```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3
Data plot for star dataset

```{r plot-star, fig.height=3, fig.width=4}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

.Calculated correlation between x and y for star dataset
 
```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4
Data plot for circle dataset

```{r, fig.height=4, fig.width=4}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(y = y, x = x)) +
  geom_point()

```
Calculated correlation between x and y for the circle dataset

```{r}
dino_data %>%
  summarize(r = cor(x, y))
```
Below are the plots of all the datasets

### Exercise 5
```{r, fig.height=7, fig.width=6}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+ geom_point()+
  facet_wrap(~ dataset, ncol = 3) + theme(legend.position = "none")
  
```
Calculated coefficients for all datasets
```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))
```
